\chapter{Introduction}

\section{Background}

A major part of learning a new language is to be able to pronounce words correctly. To be able to pronounce words correctly, a student's mouth needs to make proper movements. This is difficult to teach in a classroom setting, especially when a student needs to repeat the same phrase many times. The student can become frustrated with the teacher and not want to continue, especially if he or she feels as though he or she is being viewed as incompetent by his or her peers. However, when using a computer, the student can feel more comfortable trying the same phrase over and over without embarrassment.

Currently, there are desktop and mobile applications to help with a student's pronunciation by listening to him or her speak and providing feedback. If the student does not make the correct mouth shape, however, he or she is far less likely to pronounce the word correctly. Applications that only analyze audio can, at best, only guess what the student might be doing incorrectly with his or her mouth so these applications may not provide the help the student really needs.

\section{Solution}

Our solution is to create a mobile application to help students pronounce words correctly by not only listening to them talk and analyzing the audio, but also by watching their mouths and providing feedback for both the audio and video information. We will create an algorithm to accurately track lip movement. A generic tracking algorithm will not work for lip motion tracking since mouths change shape too much when they move. For this reason the lip tracking algorithm that we intend to implement will be specialized to mouth contours. The data provided from this software will then be combined with audio input to analyze how the student may improve his or her pronunciation. For example, the application can tell the student if he or she held his or her mouth open too long or didn't open his or her mouth enough for a particular word. In the end, this tool would make it easier and faster for students learning a new language to master correct pronunciation. 