\chapter{Technologies Used}
\label{technologies}

Below we list all of the technologies that we will be using in our system and the basic reasons why we chose to use each of them.

\section{C++}

We will be using C++ because it is a relatively efficient programming language. Additionally, it will allow us to create one library that can be cross-compiled and reused on any platform. Further, both of us have a significant amount of experience with the language.

\section{CUDA}

CUDA (Compute Unified Device Architecture) is a parallel computing platform and programming model developed by Nvidia for their GPUs. We will be using CUDA because Android devices are now starting to get dedicated GPU chips that are optimized for CUDA.

\section{Nvidia Tegra K1}

We will be using the Nvidia Tegra K1 GPU because it is the currently the most common mobile GPU being marketed, with phones like the Google Nexus 9 utilizing it.

\section{OpenCV}

We will be using the OpenCV library to do image processing such as noise filtering and edge detection. 
OpenCV also detects if there is a CUDA-capable GPU on the system and will use it if it finds one.
Additionally, it is compatible with Windows, Linux, OS X, Android, and iOS, so it will work for all of our implementations.

\section{CMake}

CMake is a cross-platform make utility which detects what compilers are installed on the system and selects an appropriate to use for the project. This will make it easy for us to test changes on different platforms by streamlining the compilation process.